
---
title: "Current Enrollment"
author: 
date: "Last Updated: 1/20/2021"
output: 
  html_document:
    theme: flatly
    toc: TRUE
---

```{r load-packages, echo=FALSE, warning=FALSE, include=FALSE, cache=FALSE}
library(magrittr)
library(codified)
library(rlang)
library(epiDisplay)
library(tibble)
library(tidyr)
library(checkmate)
library(testthat)
library(cowplot)
library(readxl)
library(knitr)
library(formattable)
library(ggpubr)
library(frequency)
library(plotly)
library(emmeans)
library(kableExtra)
library(papaja)
library(kableExtra)
library(dplyr)
library(RColorBrewer)
library(tidyverse)
library(ggformula)
library(lubridate)
library(plyr)
library(readr)
library(dplyr)
library(haven)
library(RColorBrewer)
library(ggplot2)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(reshape2)
library(skimr)
library(here)
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html", knitr.kable.NA = '') 
```


```{r Read in Files and set-up columns, echo = FALSE, warning=FALSE, message=FALSE}
#Read Masterfile
library(haven)
masterfile <- data.frame(read_sav(file = '~/Dropbox (University of Oregon)/SEAL R01/_Remote SEAL/rSEAL_Data/masterfile.sav'))

masterfile$rSEAL.C1.LDL.003[masterfile$rSEAL.C1.LDL.003 == ""] <- NA
masterfile$rSEAL.C1.LDL.029[masterfile$rSEAL.C1.LDL.029 == ""] <- NA
masterfile$rSEAL.C2.LDL.003[masterfile$rSEAL.C2.LDL.003 == ""] <- NA
masterfile$rSEAL.C2.LDL.029[masterfile$rSEAL.C2.LDL.029 == ""] <- NA
#Create new DataFrame for Enrollment Table

Enrollment <- data.frame("RSID" = masterfile$RSID,
                        "SubInfoActual"=masterfile$SubInfoStart,
                         "Survey1Actual"=masterfile$Survey1Start,
                         "Survey2Actual"=masterfile$Survey2Start,
                         "PDR2Actual"=masterfile$PDR2Start,
                         "PDR3Actual"=masterfile$PDR3Start,
                         "LENAD1DiaryActual"=masterfile$rSEAL.C1.LDL.003,
                         "LENAD2DiaryActual"=masterfile$rSEAL.C1.LDL.029,
                         "Survey3Actual"=masterfile$Survey3Start,
                         "Survey4Actual"=masterfile$Survey4Start,
                         "PDR5Actual"=masterfile$PDR5Start,
                         "PDR6Actual"=masterfile$PDR6Start,
                         "LENAD3DiaryActual"=masterfile$rSEAL.C2.LDL.003,
                         "LENAD4DiaryActual"=masterfile$rSEAL.C2.LDL.029)

```


<center>
**Wave 1 and 2 Participant Completion **  
This chart shows the combination of completions for the dyads across Waves 1 and 2.  
<center>

```{r SEAL Wave Progression, echo = FALSE, fig.width=5, fig.height=4, message=FALSE, warning=FALSE}
par(mar = c(4, 4, .2, .1))
# Format dates
masterfile$Survey1Start <- as.Date(masterfile$Survey1Start, "%Y/%m/%d")
masterfile$Survey2Start <- as.Date(masterfile$Survey2Start, "%Y/%m/%d")
masterfile$PDR2Start <- as.Date(masterfile$PDR2Start, "%Y/%m/%d")
masterfile$PDR3Start <- as.Date(masterfile$PDR3Start, "%Y/%m/%d")
#masterfile$rSEAL.C1.LDL.003 <- as.Date(masterfile$rSEAL.C1.LDL.003, "%Y/%m/%d")
#masterfile$rSEAL.C1.LDL.029 <- as.Date(masterfile$rSEAL.C1.LDL.029, "%Y/%m/%d")
masterfile$Survey3Start <- as.Date(masterfile$Survey3Start, "%Y/%m/%d")
masterfile$Survey4Start <- as.Date(masterfile$Survey4Start, "%Y/%m/%d")
masterfile$PDR5Start <- as.Date(masterfile$PDR5Start, "%Y/%m/%d")
masterfile$PDR6Start <- as.Date(masterfile$PDR6Start, "%Y/%m/%d")
#masterfile$rSEAL.C2.LDL.003 <- as.Date(masterfile$rSEAL.C2.LDL.003, "%Y/%m/%d")
#masterfile$rSEAL.C2.LDL.029 <- as.Date(masterfile$rSEAL.C2.LDL.029, "%Y/%m/%d")

#Classify Tests
Survey1Completion <- masterfile$Survey1Completion <- ifelse(masterfile$Survey1Start > "2020-07-01", "Complete", "Incomplete")
Survey2Completion <- masterfile$Survey2Completion <- ifelse(masterfile$Survey2Start > "2020-07-01", "Complete", "Incomplete")
PDR2Completion <- masterfile$PDR2Completion <- ifelse(masterfile$PDR2Start > "2020-07-01", "Complete", "Incomplete")
PDR3Completion <- masterfile$PDR3Completion<- ifelse(masterfile$PDR3Start > "2020-07-01", "Complete", "Incomplete")
LENAD1DiaryCompletion <- masterfile$LENAD1DiaryCompletion <- ifelse(masterfile$rSEAL.C1.LDL.003 > "2020-07-01", "Complete", "Incomplete")
LENAD2DiaryCompletion <- masterfile$LENAD2DiaryCompletion<- ifelse(masterfile$rSEAL.C1.LDL.029 > "2020-07-01", "Complete", "Incomplete")
Survey3Completion <- masterfile$Survey3Completion <- ifelse(masterfile$Survey3Start > "2020-07-01", "Complete", "Incomplete")
Survey4Completion <- masterfile$Survey4Completion <- ifelse(masterfile$Survey4Start > "2020-07-01", "Complete", "Incomplete")
PDR5Completion <- masterfile$PDR5Completion <- ifelse(masterfile$PDR5Start > "2020-07-01", "Complete", "Incomplete")
PDR6Completion <- masterfile$PDR6Completion<- ifelse(masterfile$PDR6Start > "2020-07-01", "Complete", "Incomplete")
LENAD3DiaryCompletion <- masterfile$LENAD3DiaryCompletion <- ifelse(masterfile$rSEAL.C2.LDL.003 > "2020-07-01", "Complete", "Incomplete")
LENAD4DiaryCompletion <- masterfile$LENAD4DiaryCompletion<- ifelse(masterfile$rSEAL.C2.LDL.029 > "2020-07-01", "Complete", "Incomplete")


Wave1_Progression <- masterfile %>%
  dplyr::mutate(month = format(Survey1Start, "%m")) %>%
  dplyr::group_by(Survey1Completion, Survey2Completion, PDR2Completion, PDR3Completion, LENAD1DiaryCompletion, LENAD2DiaryCompletion, Survey3Completion, Survey4Completion, PDR5Completion, PDR6Completion, LENAD3DiaryCompletion, LENAD4DiaryCompletion) %>%
  dplyr::summarize(Count = n())
 
  kable(Wave1_Progression,
        col.names = c("Survey 1","Survey 2","PDR 2", "PDR 3", "LENA D1 Diary", "LENA D2 Diary", "Survey 3","Survey 4","PDR 5", "PDR 6", "LENA D3 Diary", "LENA D4 Diary","Number Complete")) %>%
        kable_minimal()

```


```{r SEAL Test Counts 1, echo = FALSE, fig.width=5, fig.height=4, message=FALSE, warning=FALSE}
par(mar = c(4, 4, .2, .1))
#Counts of Variables
Survey1Start <- as.character(masterfile$Survey1Start)
Survey1Delinquent <- sum(is.na(masterfile$Survey1Start))
Survey1Complete <- length(Survey1Start) - Survey1Delinquent
Survey2Start <- as.character(masterfile$Survey2Start)
Survey2Delinquent <- sum(is.na(masterfile$Survey2Start))
Survey2Complete <- length(Survey2Start) - Survey2Delinquent
PDR2Start <- as.character(masterfile$PDR2Start)
PDR2Delinquent <- sum(is.na(masterfile$PDR2Start))
PDR2Complete <- length(PDR2Start) - Survey2Delinquent
PDR3Start <- as.character(masterfile$PDR3Start)
PDR3Delinquent <- sum(is.na(masterfile$PDR3Start))
PDR3Complete <- length(PDR3Start) - PDR3Delinquent
LENAD1Start <- as.character(masterfile$rSEAL.C1.LDL.003)
LENAD1Delinquent <- sum(is.na(masterfile$rSEAL.C1.LDL.003))
LENAD1Complete <- length(LENAD1Start) - LENAD1Delinquent
LENAD2Start <- as.character(masterfile$rSEAL.C1.LDL.029)
LENAD2Delinquent <- sum(is.na(masterfile$rSEAL.C1.LDL.029))
LENAD2Complete <- length(LENAD2Start) - LENAD2Delinquent
Survey3Start <- as.character(masterfile$Survey3Start)
Survey3Delinquent <- sum(is.na(masterfile$Survey3Start))
Survey3Complete <- length(Survey3Start) - Survey3Delinquent
Survey4Start <- as.character(masterfile$Survey4Start)
Survey4Delinquent <- sum(is.na(masterfile$Survey4Start))
Survey4Complete <- length(Survey4Start) - Survey4Delinquent
PDR5Start <- as.character(masterfile$PDR5Start)
PDR5Delinquent <- sum(is.na(masterfile$PDR5Start))
PDR5Complete <- length(PDR5Start) - Survey4Delinquent
PDR6Start <- as.character(masterfile$PDR6Start)
PDR6Delinquent <- sum(is.na(masterfile$PDR6Start))
PDR6Complete <- length(PDR6Start) - PDR6Delinquent
LENAD3Start <- as.character(masterfile$rSEAL.C2.LDL.003)
LENAD3Delinquent <- sum(is.na(masterfile$rSEAL.C2.LDL.003))
LENAD3Complete <- length(LENAD3Start) - LENAD3Delinquent
LENAD4Start <- as.character(masterfile$rSEAL.C2.LDL.029)
LENAD4Delinquent <- sum(is.na(masterfile$rSEAL.C2.LDL.029))
LENAD4Complete <- length(LENAD4Start) - LENAD4Delinquent

# Create data
data <- data.frame(
  Wave1=c("Survey 1","Survey 2","PDR 2","PDR 3","LENA Day 1 Diary", "LENA Day 2 Diary", "Survey 3","Survey 4","PDR 5","PDR 6","LENA Day 3 Diary", "LENA Day 4 Diary") ,  
  value=c(Survey1Complete,Survey2Complete,PDR2Complete,PDR3Complete,LENAD1Complete, LENAD2Complete,Survey3Complete,Survey4Complete,PDR5Complete,PDR6Complete,LENAD3Complete, LENAD4Complete)
  )
tbl <- kbl(data, col.names = c("Instrument","Counts")) %>%
  kable_styling( bootstrap_options = "striped", full_width = F, position = "float_left", font_size = 16)

```
<center>
**Wave 1 and 2 Participant Progression **  
This chart shows the number of participants complete with each survey instrument across Wave 1 and 2. Delinquent in this case is currently defined as being greater than 14 days from when they completed a subjectinfo form, and no completion record for the given instrument. This does not currently capture those who have dropped out (but can/will), but is set-up to show when a participant is within 7 days and 7-14 days from when the subject info was offered. We can also set up specific ranges by instrument for delayed or delinquent statuses.   
<center>
::: {}
```{r SEAL Wave 1 Progression, echo = FALSE, fig.width=10, fig.height=4, message=FALSE, warning=FALSE}
Enrollment$Surv1CompletionTime<- round(difftime(Enrollment$Survey1Actual,Enrollment$SubInfoActual, units = c("days"),1))
today <- Sys.time()
start <- as.Date("2020-07-01")
Test <- today - Enrollment$SubInfoActual
Enrollment2 <- Enrollment %>%
      select(RSID:Surv1CompletionTime) %>%
      mutate(
      Surv1Status = case_when(
      Test > 14 & is.na(Survey1Actual) ~ "Delinquent",
      Test < 7 & is.na(Survey1Actual) ~ "On-Track",
      Survey1Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )
Enrollment3 <- Enrollment2%>%
      select(RSID:Surv1Status) %>%
      mutate(
      Surv2Status = case_when(
      Test > 14 & is.na(Survey2Actual) ~ "Delinquent",
      Test < 7 & is.na(Survey2Actual) ~ "On-Track",
      Survey2Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )
Enrollment4 <- Enrollment3%>%
      select(RSID:Surv2Status) %>%
      mutate(
      PDR2Status = case_when(
      Test > 14 & is.na(PDR2Actual) ~ "Delinquent",
      Test < 7 & is.na(PDR2Actual) ~ "On-Track",
      PDR2Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )
Enrollment5 <- Enrollment4%>%
      select(RSID:PDR2Status) %>%
      mutate(
      PDR3Status = case_when(
      Test > 14 & is.na(PDR3Actual) ~ "Delinquent",
      Test < 7 & is.na(PDR3Actual) ~ "On-Track",
      PDR3Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )
Enrollment6 <- Enrollment5%>%
      select(RSID:PDR3Status) %>%
      mutate(
      LENAD1DiaryStatus = case_when(
      Test > 14 & is.na(LENAD1DiaryActual) ~ "Delinquent",
      Test < 7 & is.na(LENAD1DiaryActual) ~ "On-Track",
      LENAD1DiaryActual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )
Enrollment7 <- Enrollment6%>%
      select(RSID:LENAD1DiaryStatus) %>%
      mutate(
      LENAD2DiaryStatus = case_when(
      Test > 14 & is.na(LENAD2DiaryActual) ~ "Delinquent",
      Test < 7 & is.na(LENAD2DiaryActual) ~ "On-Track",
      LENAD2DiaryActual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )

Enrollment8 <- Enrollment7%>%
      select(RSID:LENAD2DiaryStatus) %>%
      mutate(
      Surv3Status = case_when(
      Test > 14 & is.na(Survey3Actual) ~ "Delinquent",
      Test < 7 & is.na(Survey3Actual) ~ "On-Track",
      Survey3Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )

Enrollment9 <- Enrollment8%>%
      select(RSID:Surv3Status) %>%
      mutate(
      Surv4Status = case_when(
      Test > 14 & is.na(Survey4Actual) ~ "Delinquent",
      Test < 7 & is.na(Survey4Actual) ~ "On-Track",
      Survey4Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )

Enrollment10 <- Enrollment9%>%
      select(RSID:Surv4Status) %>%
      mutate(
      PDR5Status = case_when(
      Test > 14 & is.na(PDR5Actual) ~ "Delinquent",
      Test < 7 & is.na(PDR5Actual) ~ "On-Track",
      PDR5Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )

Enrollment11 <- Enrollment10%>%
      select(RSID:PDR5Status) %>%
      mutate(
      PDR6Status = case_when(
      Test > 14 & is.na(PDR6Actual) ~ "Delinquent",
      Test < 7 & is.na(PDR6Actual) ~ "On-Track",
      PDR6Actual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )

Enrollment12 <- Enrollment11%>%
      select(RSID:PDR6Status) %>%
      mutate(
      LENAD3DiaryStatus = case_when(
      Test > 14 & is.na(LENAD3DiaryActual) ~ "Delinquent",
      Test < 7 & is.na(LENAD3DiaryActual) ~ "On-Track",
      LENAD3DiaryActual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )

Enrollment13 <- Enrollment12%>%
      select(RSID:LENAD3DiaryStatus) %>%
      mutate(
      LENAD4DiaryStatus = case_when(
      Test > 14 & is.na(LENAD4DiaryActual) ~ "Delinquent",
      Test < 7 & is.na(LENAD4DiaryActual) ~ "On-Track",
      LENAD4DiaryActual > start       ~ "Complete",
      TRUE                      ~ "Yellow"
      )
     )


Enrollment14 <- gather(Enrollment13, "Instrument", "Status", Surv1Status, Surv2Status,PDR2Status, PDR3Status,LENAD1DiaryStatus,LENAD2DiaryStatus,Surv3Status, Surv4Status,PDR5Status, PDR6Status,LENAD3DiaryStatus,LENAD4DiaryStatus,)
library(ggplot2) #load ggplot2 library
Enrollment14$Cases <- factor(Enrollment14$RSID) # Create a categorical variable
Enrollment14$Instrument <- factor(Enrollment14$Instrument, levels = c("Surv1Status","Surv2Status","PDR2Status","PDR3Status", "LENAD1DiaryStatus","LENAD2DiaryStatus", "Surv3Status","Surv4Status","PDR5Status","PDR6Status", "LENAD3DiaryStatus","LENAD4DiaryStatus")) # Create categorical variable
p <- ggplot(data = Enrollment14, aes(x=Instrument, fill=Status) ) + geom_bar() + # Creates stacked bar chart
scale_x_discrete(labels=c("Survey 1", "Survey 2", "PDR2", "PDR3", "LENA D1 Diary", "LENA D2 Diary", "Survey 3", "Survey 4", "PDR5", "PDR6", "LENA D3 Diary", "LENA D4 Diary")) +
scale_fill_discrete(labels = c("Complete", "Delinquent")) #Manually assigns colors
p <- p + xlab("Instrument") + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + labs(fill = "Statuses") 
 # Adds title and labels
p
```

```{r SEAL Wave 1 Progression Table, echo = FALSE, fig.width=5, fig.height=4, message=FALSE, warning=FALSE}
Wave1 <- table(Enrollment14$Instrument, Enrollment14$Status, dnn=c("Instrument", "Status"))
library(kableExtra)
rownames(Wave1) = c("Survey 1", "Survey 2", "PDR2", "PDR3", "LENA D1 Diary", "LENA D2 Diary", "Survey 3", "Survey 4", "PDR5", "PDR6", "LENA D3 Diary", "LENA D4 Diary")
Wave1Counts <- kable(Wave1,
        col.names = c("Complete","Delinquent")) %>%
        kable_minimal()
Wave1Counts
```
:::