
---
title: "Current Enrollment"
author: 
date: "Last Updated: 3/5/2021, 10:45pm"
output: 
  html_document:
    theme: flatly
    toc: TRUE
---

```{r load-packages, echo=FALSE, warning=FALSE, include=FALSE, message = FALSE, cache=FALSE}
if(!require(magrittr)) install.packages("magrittr",repos = "http://cran.us.r-project.org")
if(!require(codified)) install.packages("codified",repos = "http://cran.us.r-project.org")
if(!require(rlang)) install.packages("rlang",repos = "http://cran.us.r-project.org")
if(!require(epiDisplay)) install.packages("epiDisplay",repos = "http://cran.us.r-project.org")
if(!require(forcats)) install.packages("forcats",repos = "http://cran.us.r-project.org")
if(!require(tibble)) install.packages("tibble",repos = "http://cran.us.r-project.org")
if(!require(tidyr)) install.packages("tidyr",repos = "http://cran.us.r-project.org")
if(!require(checkmate)) install.packages("checkmate",repos = "http://cran.us.r-project.org")
if(!require(testthat)) install.packages("testthat",repos = "http://cran.us.r-project.org")
if(!require(cowplot)) install.packages("cowplot",repos = "http://cran.us.r-project.org")
if(!require(readxl)) install.packages("readxl",repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr",repos = "http://cran.us.r-project.org")
if(!require(formattable)) install.packages("formattable",repos = "http://cran.us.r-project.org")
if(!require(ggpubr)) install.packages("ggpubr",repos = "http://cran.us.r-project.org")
if(!require(frequency)) install.packages("frequency",repos = "http://cran.us.r-project.org")
if(!require(plotly)) install.packages("plotly",repos = "http://cran.us.r-project.org")
if(!require(emmeans)) install.packages("emmeans",repos = "http://cran.us.r-project.org")
if(!require(kableExtra)) install.packages("KableExtra",repos = "http://cran.us.r-project.org")
if(!require(papaja)) install.packages("papaja",repos = "http://cran.us.r-project.org")
if(!require(dplyr)) install.packages("dplyr",repos = "http://cran.us.r-project.org")
if(!require(RColorBrewer)) install.packages("RColorBrewer",repos = "http://cran.us.r-project.org")
if(!require(tidyverse)) install.packages("tidyverse",repos = "http://cran.us.r-project.org")
if(!require(ggformula)) install.packages("ggformula",repos = "http://cran.us.r-project.org")
if(!require(lubridate)) install.packages("lubridate",repos = "http://cran.us.r-project.org")
if(!require(plyr)) install.packages("plyr",repos = "http://cran.us.r-project.org")
if(!require(readr)) install.packages("readr",repos = "http://cran.us.r-project.org")
if(!require(dplyr)) install.packages("dplyr",repos = "http://cran.us.r-project.org")
if(!require(haven)) install.packages("haven",repos = "http://cran.us.r-project.org")
if(!require(ggplot2)) install.packages("ggplot2",repos = "http://cran.us.r-project.org")
if(!require(DiagrammeR)) install.packages("DiagrammeR",repos = "http://cran.us.r-project.org")
if(!require(DiagrammeRsvg)) install.packages("DiagrammeRsvg",repos = "http://cran.us.r-project.org")
#if(!require(rsvg)) install.packages("rsvg",repos = "http://cran.us.r-project.org")
if(!require(reshape2)) install.packages("reshape2",repos = "http://cran.us.r-project.org")
if(!require(skimr)) install.packages("skimr",repos = "http://cran.us.r-project.org")
if(!require(here)) install.packages("here",repos = "http://cran.us.r-project.org")
if(!require(xlsx)) install.packages("xlsx",repos = "http://cran.us.r-project.org")
if(!require(rio)) install.packages("rio",repos = "http://cran.us.r-project.org")
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html", knitr.kable.NA = '') 
```


```{r Read in Files and set-up columns, echo=FALSE, warning=FALSE, include=FALSE, message = FALSE, cache=FALSE}

#Read Masterfile
library(haven)
library(boxr)
library(rio)
library(readxl)
box_auth_service()
box_setwd(132211861740)
masterfile <- data.frame(read_sav(file = box_dl(779383318727, overwrite = TRUE)))
#LENA Data
LENADataW1 <- data.frame(read_xlsx(box_dl(786237121897, overwrite = TRUE)))
LENADataW2 <- data.frame(read_xlsx(box_dl(786236300573, overwrite = TRUE)))                     
#rSEAL Manual Consent Data
Consents1 <- data.frame(read_xlsx(box_dl(779380836611, overwrite = TRUE))) 
#rSEAL Consent Tracker
Consents2 <- data.frame(read.csv(file = box_dl(785633108805, overwrite = TRUE)))
Consents2 <- subset(Consents2, select = -c(2:17))
Consents2$recontact <- as.numeric(Consents2$recontact)

#Read in LENA Tracker for Expected Dates
LENATracker1 <- data.frame(read.csv(box_dl(786241215058, overwrite = TRUE)))
LENATracker2 <- data.frame(read.csv(box_dl(786237496379, overwrite = TRUE)))
LENATracker3 <- data.frame(read.csv(box_dl(786240935751, overwrite = TRUE)))
#Read in Case Progression Log
CaseProg <- data.frame(read.csv(file = box_dl(785626649189, overwrite = TRUE)))

#Read in Fidelity Data
FIND <- data.frame(read_sav(file = box_dl(786242280747, overwrite = TRUE)))
HTP <- data.frame(read_sav(file = box_dl(786243081157, overwrite = TRUE)))

#Read in Coach Impressions
CoachImp <- data.frame(read_sav(file = box_dl(786245463583, overwrite = TRUE)))

LENATracker1$LENA1Expected <- as.Date(LENATracker1$ExpectedDt1 , "%Y-%m-%d")
LENATracker1$LENA2Expected <- as.Date(LENATracker1$ExpectedDt2 , "%Y-%m-%d")
LENATracker2$LENA3Expected <- as.Date(LENATracker2$ExpectedDt1 , "%Y-%m-%d")
LENATracker2$LENA4Expected <- as.Date(LENATracker2$ExpectedDt2 , "%Y-%m-%d")
LENATracker3$LENA5Expected <- as.Date(LENATracker3$ExpectedDt1 , "%Y-%m-%d")
LENATracker3$LENA6Expected <- as.Date(LENATracker3$ExpectedDt2 , "%Y-%m-%d")

LENATracker <- left_join(LENATracker1,LENATracker2, by = "RSID")
LENATracker <- left_join(LENATracker,LENATracker3, by = "RSID")

# Format dates
masterfile$SubInfoStart <- as.Date(masterfile$SubInfoStart, "%Y/%m/%d")
masterfile$Survey1Start <- as.Date(masterfile$Survey1Start, "%Y/%m/%d")
masterfile$Survey2Start <- as.Date(masterfile$Survey2Start, "%Y/%m/%d")
masterfile$PDR2Start <- as.Date(masterfile$PDR2Start, "%Y/%m/%d")
masterfile$PDR3Start <- as.Date(masterfile$PDR3Start, "%Y/%m/%d")
masterfile$Survey3Start <- as.Date(masterfile$Survey3Start, "%Y/%m/%d")
masterfile$Survey4Start <- as.Date(masterfile$Survey4Start, "%Y/%m/%d")
masterfile$PDR5Start <- as.Date(masterfile$PDR5Start, "%Y/%m/%d")
masterfile$PDR6Start <- as.Date(masterfile$PDR6Start, "%Y/%m/%d")
masterfile$rSEAL.C2.LDL.003 <- as.Date(masterfile$rSEAL.C2.LDL.003, "%Y-%m-%d")
masterfile$rSEAL.C2.LDL.029 <- as.Date(masterfile$rSEAL.C2.LDL.029, "%Y-%m-%d")
masterfile$rSEAL.C1.LDL.003 <- as.Date(masterfile$rSEAL.C1.LDL.003, "%Y-%m-%d")
masterfile$rSEAL.C1.LDL.029 <- as.Date(masterfile$rSEAL.C1.LDL.029, "%Y-%m-%d")
FIND$StartDate <- as.Date(FIND$StartDate, "%Y-%m-%d")
HTP$StartDate <- as.Date(HTP$StartDate, "%Y-%m-%d")
CaseProg$Q2_1_TEXT <- as.Date(CaseProg$Q2_1_TEXT,"%m/%d/%y")
CaseProg$Q2_2_TEXT <- as.Date(CaseProg$Q2_2_TEXT,"%m/%d/%y")
CaseProg$Q2_3_TEXT <- as.Date(CaseProg$Q2_3_TEXT,"%m/%d/%y")
CaseProg$Q2_4_TEXT <- as.Date(CaseProg$Q2_4_TEXT,"%m/%d/%y")                       
CaseProg$Q2_10_TEXT <- as.Date(CaseProg$Q2_10_TEXT,"%m/%d/%y")
CaseProg$Q2_11_TEXT <- as.Date(CaseProg$Q2_11_TEXT,"%m/%d/%y")
CaseProg$Q2_12_TEXT <- as.Date(CaseProg$Q2_12_TEXT,"%m/%d/%y")            
CaseProg$Q2_14_TEXT <- as.Date(CaseProg$Q2_14_TEXT,"%m/%d/%y") 
CaseProg$Q2_15_TEXT <- as.Date(CaseProg$Q2_15_TEXT,"%m/%d/%y")
CaseProg$Q2_16_TEXT <- as.Date(CaseProg$Q2_16_TEXT,"%m/%d/%y")
CaseProg$Q2_17_TEXT <- as.Date(CaseProg$Q2_17_TEXT,"%m/%d/%y")
CaseProg$Q2_18_TEXT <- as.Date(CaseProg$Q2_18_TEXT,"%m/%d/%y")            
CaseProg$Q2_19_TEXT <- as.Date(CaseProg$Q2_19_TEXT,"%m/%d/%y")      
CaseProg$Q2_20_TEXT <- as.Date(CaseProg$Q2_20_TEXT,"%m/%d/%y")                    
CaseProg$Q2_21_TEXT <- as.Date(CaseProg$Q2_21_TEXT,"%m/%d/%y") 
CaseProg$Q2_22_TEXT <- as.Date(CaseProg$Q2_22_TEXT,"%m/%d/%y")                       
CaseProg$Q2_23_TEXT <- as.Date(CaseProg$Q2_23_TEXT,"%m/%d/%y")                      
CaseProg$Q2_24_TEXT <- as.Date(CaseProg$Q2_24_TEXT,"%m/%d/%y")
CaseProg$Q9 <- as.numeric(CaseProg$Q9)
CaseProg$Q10 <- as.Date(CaseProg$Q10,"%m/%d/%y")
CoachImp$StartDate <- as.Date(CoachImp$StartDate,"%m/%d/%y")
CoachImp$EndDate <- as.Date(CoachImp$EndDate,"%m/%d/%y")
CoachImp$RecordedDate <- as.Date(CoachImp$RecordedDate,"%m/%d/%y")
LENADataW1$D1_OptOut <- as.Date(LENADataW1$D1_OptOut , "%Y-%m-%d")
LENADataW1$D2_OptOut <- as.Date(LENADataW1$D2_OptOut , "%Y-%m-%d")
LENADataW2$D1_OptOut <- as.Date(LENADataW2$D1_OptOut , "%Y-%m-%d")
LENADataW2$D2_OptOut <- as.Date(LENADataW2$D2_OptOut , "%Y-%m-%d")

#Remove rows without cases
library(dplyr)
#CaseProg <- CaseProg %>% slice(-c(1,2))
CoachImp <- CoachImp %>% slice(-c(1,2))
FIND <- FIND %>% slice(-c(78))
#Remove test response RS200 from CaseProg
CaseProg <- CaseProg %>% slice(-c(28))
#Edit date for drop out for RS027 since in wrong format
CaseProg[CaseProg$RSID == "RS027", "DropOutDate"] <- "12/31/20"
#Remove duplicate response RS039 
CoachImp <- CoachImp %>% slice(-c(14))
Staff.Signature <- Consents2$Staff.Signature <- ifelse(Consents2$Completed == "2",(as.character(Consents2$StartDate)), "NA")
Consents2$Staff.Signature <- as.Date(Consents2$Staff.Signature,"%Y-%m-%d" )
Informed.consent <- Consents2$Informed.consent <- ifelse(Consents2$Completed == "1",(as.character(Consents2$StartDate)), "NA")
Consents2$Informed.consent <- as.Date(Consents2$Informed.consent,"%Y-%m-%d" )
Recontact <- Consents2$recontact <- ifelse(Consents2$recontact == 1 ,"Signed", "NA")

#Create new DataFrame for Enrollment Table
Enrollment <- data.frame("RSID" = masterfile$RSID,
                        "SubInfoActual"=masterfile$SubInfoStart,
                         "Survey1Actual"=masterfile$Survey1Start,
                         "Survey2Actual"=masterfile$Survey2Start,
                         "PDR2Actual"=masterfile$PDR2Start,
                         "PDR3Actual"=masterfile$PDR3Start,
                         "LENAD1DiaryActual"=masterfile$LENAD1Start,
                         "LENAD2DiaryActual"=masterfile$LENAD2Start,
                         "Survey3Actual"=masterfile$Survey3Start,
                         "Survey4Actual"=masterfile$Survey4Start,
                         "PDR5Actual"=masterfile$PDR5Start,
                         "PDR6Actual"=masterfile$PDR6Start,
                         "LENAD3DiaryActual"=masterfile$LENAD3Start,
                         "LENAD4DiaryActual"=masterfile$LENAD4Start)
                        
Consents1 <- data.frame("RSID" = Consents1$RSID,
                        "Informed Consent"= Consents1$Informed.consent, 
                        "Recontact" = Consents1$Recontact,
                        "StaffSignature"= Consents1$Staff.Signature)
Consents2 <- data.frame("RSID" = Consents2$RSID,
                        "Informed Consent"= Consents2$Informed.consent, 
                        "Recontact" = Consents2$recontact,
                        "StaffSignature"= Consents2$Staff.Signature)

FIND <- data.frame("RSID" = FIND$rSEAL.R1.FFC.001,
                        "FidelityDate"= FIND$StartDate, 
                        "IntvSessionComp" = FIND$rSEAL.R1.FFC.002)

HTP <- data.frame("RSID" = HTP$rSEAL.R1.HFC.001,
                        "FidelityDate"= HTP$StartDate, 
                        "IntvSessionComp" = HTP$rSEAL.R1.HFC.002)

#Select only session 10 cases and format RSID's
FIND <- FIND[FIND$IntvSessionComp == 10,]
HTP <- HTP[HTP$IntvSessionComp == 10,]
Fidelity <- full_join(FIND,HTP)
Fidelity$RSID <- str_pad(Fidelity$RSID, width=3, side="left", pad="0")
Fidelity$RSID <- paste("RS", Fidelity$RSID,sep="")

#Select/merge consent data to align to just one case
Consents2.1 <- Consents2[rowSums(is.na(Consents2)) < 3, ]
Consents2.2 <- Consents2.1[match(unique(Consents2.1$RSID), Consents2.1$RSID),]
Consents2.3 <- data.frame("RSID" = Consents2.2$RSID,
                        "Informed Consent"= Consents2.2$Informed.Consent)
Consents2.4 <- Consents2.1[match(unique(Consents2.1$StaffSignature), Consents2.1$StaffSignature),]
Consents2.5 <- data.frame("RSID" = Consents2.4$RSID,
                        "StaffSignature"= Consents2.4$StaffSignature)
Consents2.6 <- Consents2.5[!is.na(Consents2.5[, 2]), ]
Consents2.7 <- Consents2.3[!is.na(Consents2.3[, 2]), ]

Consents4 <- Consents2.1[!is.na(Consents2.1[, 3]), ]
Consents4.2 <- Consents4[match(unique(Consents4$RSID), Consents4$RSID),]
Consents4.3 <- data.frame("RSID" = Consents4.2$RSID,
                        "Recontact"= Consents4.2$Recontact)

Consents3 <- full_join(Consents2.6,Consents2.7)
Consents5 <- left_join(Consents3,Consents4.3)

LENATracker <- data.frame("RSID" = LENATracker$RSID,
                        "LENA1Expected" = LENATracker$LENA1Expected,
                        "LENA2Expected"= LENATracker$LENA2Expected,
                        "LENA3Expected"= LENATracker$LENA3Expected,
                        "LENA4Expected"= LENATracker$LENA4Expected,
                        "LENA5Expected"= LENATracker$LENA5Expected,
                        "LENA6Expected"= LENATracker$LENA6Expected)
LENADataW1 <- data.frame("RSID" = LENADataW1$RSID,
                        "LENAD1DataW1" = LENADataW1$FullHours_D1,
                        "LENAD2DataW1"= LENADataW1$FullHours_D2,
                        "LENAD1OptOut"= LENADataW1$D1_OptOut,
                        "LENAD2OptOut"= LENADataW1$D2_OptOut)
LENADataW2 <- data.frame("RSID" = LENADataW2$RSID,
                        "LENAD1DataW2" = LENADataW2$FullHours_D1,
                        "LENAD2DataW2"= LENADataW2$FullHours_D2,
                        "LENAD3OptOut"= LENADataW2$D1_OptOut,
                        "LENAD4OptOut"= LENADataW2$D2_OptOut)
LENADataW2 <- LENADataW2[match(unique(LENADataW2$RSID), LENADataW2$RSID),]
CaseProg <- data.frame("RSID" = CaseProg$ExternalReference,
                        "Survey1_OptOut" = CaseProg$Q2_1_TEXT,
                        "Survey2_OptOut" = CaseProg$Q2_2_TEXT,
                        "PDRW1D2_OptOut" = CaseProg$Q2_3_TEXT,
                        "PDRW1D3_OptOut" = CaseProg$Q2_4_TEXT,
                        "LENAW1D1Log_OptOut" = CaseProg$Q2_10_TEXT,
                        "LENAW1D2Log_OptOut" = CaseProg$Q2_11_TEXT,
                        "Survey3_OptOut" = CaseProg$Q2_12_TEXT,
                        "Survey4_OptOut" = CaseProg$Q2_14_TEXT,
                        "PDRW2D2_OptOut" = CaseProg$Q2_15_TEXT,
                        "PDRW2D3_OptOut" = CaseProg$Q2_16_TEXT,
                        "LENAW2D1Log_OptOut" = CaseProg$Q2_17_TEXT,
                        "LENAW2D2Log_OptOut" = CaseProg$Q2_18_TEXT,
                        "Survey5_OptOut" = CaseProg$Q2_19_TEXT,
                        "Survey6_OptOut" = CaseProg$Q2_20_TEXT,
                        "PDRW3D2_OptOut" = CaseProg$Q2_21_TEXT,
                        "PDRW3D3_OptOut" = CaseProg$Q2_22_TEXT,
                        "LENAW3D1Log_OptOut" = CaseProg$Q2_23_TEXT,
                        "LENAW3D2Log_OptOut" = CaseProg$Q2_24_TEXT,
                        "DropOutStage" = CaseProg$Q9,
                        "DropOutDate" = CaseProg$Q10)
CoachImp <- data.frame("RSID" = CoachImp$RSID,
                        "CoachImpComplete" = CoachImp$RecordedDate)
EnrollmentConsents <- full_join(Consents1,Consents5)
#Remove duplicate response from RS018, RS046, RS062, RS064
EnrollmentConsents <- EnrollmentConsents %>% slice(-c(42,43, 44,48))

EnrollmentConsents <- full_join(EnrollmentConsents,CoachImp)
#Remove duplicate response from RS039, RS005
EnrollmentConsents <- EnrollmentConsents %>% slice(-c(29,48))
#Fix duplicates
EnrollmentConsents[EnrollmentConsents$RSID=="RS005","StaffSignature"] <- "2021-02-23"


EnrollmentConsents <- full_join(EnrollmentConsents,LENADataW1)
EnrollmentConsents <- full_join(EnrollmentConsents,LENADataW2)
EnrollmentConsents <- left_join(EnrollmentConsents,LENATracker, by = "RSID")
EnrollmentConsents <- left_join(EnrollmentConsents,Fidelity, by = "RSID")
EnrollmentConsents <- left_join(EnrollmentConsents,CaseProg, by = "RSID")
library(dplyr)
Enrollment <- left_join(EnrollmentConsents, Enrollment)
```

```{r SEAL Counts by Wave, echo = FALSE, fig.width=5, fig.height=4, message=FALSE, warning=FALSE}
par(mar = c(4, 4, .2, .1))

#Enrollment$Surv1CompletionTime<- #round(difftime(Enrollment$Survey1Actual,Enrollment$SubInfoActual, units = c("days"),1))
today <- as.Date(Sys.time())
start <- as.Date("2020-07-01")
Test0 <- today - as.Date(Enrollment$Informed.Consent,"%y-%m-%d")
Test <- today - as.Date(Enrollment$SubInfoActual, "%y-%m-%d")
Test1 <- today - as.Date(Enrollment$Survey1Actual, "%y-%m-%d")
Test2 <- today - as.Date(Enrollment$Survey2Actual, "%y-%m-%d")
Test3 <- today - as.Date(Enrollment$PDR2Actual, "%y-%m-%d")
Test4 <- today - as.Date(Enrollment$LENA1Expected, "%y-%m-%d")
Test4.1 <- today - as.Date(Enrollment$LENAD1DiaryActual, "%y-%m-%d")
Test5 <- today - as.Date(Enrollment$LENA2Expected, "%y-%m-%d")
Test5.1 <- today - as.Date(Enrollment$LENAD2DiaryActual, "%y-%m-%d")
Test6 <- today - as.Date(Enrollment$FidelityDate, "%y-%m-%d")
Test7 <- today - as.Date(Enrollment$Survey3Actual, "%y-%m-%d")
Test8 <- today - as.Date(Enrollment$Survey4Actual, "%y-%m-%d")
Test9 <- today - as.Date(Enrollment$PDR5Actual, "%y-%m-%d")
Test10 <- today - as.Date(Enrollment$LENA3Expected, "%y-%m-%d")
Test11 <- today - as.Date(Enrollment$LENAD3DiaryActual, "%y-%m-%d")
Test11.1 <- today - as.Date(Enrollment$LENA4Expected, "%y-%m-%d")
Enrollment1 <- Enrollment %>%
      select(RSID:LENAD4DiaryActual) %>%
      mutate(
      ConsentStatus = case_when(is.na(Enrollment$Informed.Consent) ~ "Delinquent",
      Enrollment$Informed.Consent > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment1.1 <- Enrollment1 %>%
        select(RSID:ConsentStatus) %>%
      mutate(
      PostConsentStatus = case_when(
      DropOutStage > 0 & is.na(Enrollment$SubInfoActual) ~ "Opt-Out",
      Test0 > 7 & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      Test0 <= 7 & Test0 >= 3 & is.na(Enrollment$SubInfoActual) ~ "Warning",
      Test0 < 3 & is.na(Enrollment$SubInfoActual) ~ "On-Track",
      Survey1Actual > start & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      Survey2Actual > start & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      PDR2Actual > start & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      PDR3Actual > start & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      LENAD1DiaryActual > start & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      LENAD2DiaryActual > start & is.na(Enrollment$SubInfoActual) ~ "Delinquent",
      SubInfoActual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment2 <- Enrollment1.1 %>%
      select(RSID:PostConsentStatus) %>%
      mutate(
      Surv1Status = case_when(
      DropOutStage > 0 & is.na(Survey1Actual) ~ "Opt-Out",
      Survey1_OptOut > start  ~ "Opt-Out",
      Test > 7 & is.na(Survey1Actual) ~ "Delinquent",
      Test <= 7 & Test >= 3 & is.na(Survey1Actual) ~ "Warning",
      Test < 3 & is.na(Survey1Actual) ~ "On-Track",
      Survey2Actual > start & is.na(Survey1Actual) ~ "Delinquent",
      PDR2Actual > start & is.na(Survey1Actual) ~ "Delinquent",
      PDR3Actual > start & is.na(Survey1Actual) ~ "Delinquent",
      LENAD1DiaryActual > start & is.na(Survey1Actual) ~ "Delinquent",
      LENAD2DiaryActual > start & is.na(Survey1Actual) ~ "Delinquent",
      Survey1Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment3 <- Enrollment2%>%
      select(RSID:Surv1Status) %>%
      mutate(
      Surv2Status = case_when(
      DropOutStage > 0 & is.na(Survey2Actual) ~ "Opt-Out",
      Survey2_OptOut > start  ~ "Opt-Out",
      Test1 > 7 & is.na(Survey2Actual) ~ "Delinquent",
      Test1 <= 7 & Test1 >= 3 & is.na(Survey2Actual) ~ "Warning",
      Test1 < 3 & is.na(Survey2Actual) ~ "On-Track",
      PDR2Actual > start & is.na(Survey2Actual) ~ "Delinquent",
      PDR3Actual > start & is.na(Survey2Actual) ~ "Delinquent",
      LENAD1DiaryActual > start & is.na(Survey2Actual) ~ "Delinquent",
      LENAD2DiaryActual > start & is.na(Survey2Actual) ~ "Delinquent",
      Survey2Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment4 <- Enrollment3%>%
      select(RSID:Surv2Status) %>%
      mutate(
      PDR2Status = case_when(
      DropOutStage > 0 & is.na(PDR2Actual) ~ "Opt-Out",
      PDRW1D2_OptOut > start  ~ "Opt-Out",
      Test2 > 3 & is.na(PDR2Actual) ~ "Delinquent",
      Test2 <= 3 & Test2 >= 1 & is.na(PDR2Actual) ~ "Warning",
      Test2 < 1 & is.na(PDR2Actual) ~ "On-Track",
      PDR3Actual > start & is.na(PDR2Actual) ~ "Delinquent",
      LENAD1DiaryActual > start & is.na(PDR2Actual) ~ "Delinquent",
      LENAD2DiaryActual > start & is.na(PDR2Actual) ~ "Delinquent",
      PDR2Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment5 <- Enrollment4%>%
      select(RSID:PDR2Status) %>%
      mutate(
      PDR3Status = case_when(
      DropOutStage > 0 & is.na(PDR3Actual) ~ "Opt-Out",
      PDRW1D3_OptOut > start  ~ "Opt-Out",
      Test3 > 3 & is.na(PDR3Actual) ~ "Delinquent",
      Test3 <= 3 & Test3 >= 1 & is.na(PDR3Actual) ~ "Warning",
      Test3 < 1 & is.na(PDR3Actual) ~ "On-Track",
      LENAD1DiaryActual > start & is.na(PDR3Actual) ~ "Delinquent",
      LENAD2DiaryActual > start & is.na(PDR3Actual) ~ "Delinquent",
      PDR3Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment6 <- Enrollment5%>%
      select(RSID:PDR3Status) %>%
      mutate(
      LENAD1DiaryStatus = case_when(
      DropOutStage > 0 & is.na(LENAD1DiaryActual) ~ "Opt-Out",
      LENAW1D1Log_OptOut > start  ~ "Opt-Out",
      Test4 > 3 & is.na(LENAD1DiaryActual) ~ "Delinquent",
      Test4 <= 3 & Test4 >= 1 & is.na(LENAD1DiaryActual) ~ "Warning",
      Test4 < 1 & is.na(LENAD1DiaryActual) ~ "On-Track",
      LENAD2DiaryActual > start & is.na(LENAD1DiaryActual) ~ "Delinquent",
      LENAD1DiaryActual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment6.1 <- Enrollment6%>%
      select(RSID:LENAD1DiaryStatus) %>%
      mutate(
      LENAD1DataStatus = case_when(
      DropOutStage > 0 & is.na(LENAD1DataW1) ~ "Opt-Out",
      Enrollment6$LENAD1OptOut > start & is.na(LENAD1DataW1) ~ "Opt-Out",
      Test4 > 21 & is.na(LENAD1DataW1) ~ "Delinquent",
      Test4 <= 21 & Test4 >= 14 & is.na(LENAD1DataW1) ~ "Warning",
      Test4 < 14 & is.na(LENAD1DataW1) ~ "On-Track",
      LENAD2DiaryActual > start & is.na(LENAD1DataW1) ~ "Delinquent",
      LENAD1DataW1 > 0       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment7 <- Enrollment6.1%>%
      select(RSID:LENAD1DataStatus) %>%
      mutate(
      LENAD2DiaryStatus = case_when(
      DropOutStage > 0 & is.na(LENAD2DiaryActual) ~ "Opt-Out",
      LENAW1D2Log_OptOut > start  ~ "Opt-Out",
      Test5 > 3 & is.na(LENAD2DiaryActual) ~ "Delinquent",
      Test5 <= 3 & Test5 >= 1 & is.na(LENAD2DiaryActual) ~ "Warning",
      Test5 < 1 & is.na(LENAD2DiaryActual) ~ "On-Track",
      Survey3Actual > start & is.na(LENAD2DiaryActual) ~ "Delinquent",
      Survey4Actual > start & is.na(LENAD2DiaryActual) ~ "Delinquent",
      PDR5Actual > start & is.na(LENAD2DiaryActual) ~ "Delinquent",
      PDR6Actual > start & is.na(LENAD2DiaryActual) ~ "Delinquent",
      LENAD3DiaryActual > start & is.na(LENAD2DiaryActual) ~ "Delinquent",
      LENAD4DiaryActual > start & is.na(LENAD2DiaryActual) ~ "Delinquent",
      LENAD2DiaryActual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment7.1 <- Enrollment7%>%
      select(RSID:LENAD2DiaryStatus) %>%
      mutate(
      LENAD2DataStatus = case_when(
      DropOutStage > 0 & is.na(LENAD2DataW1) ~ "Opt-Out",
      Enrollment7$LENAD2OptOut > start & is.na(LENAD2DataW1) ~ "Opt-Out",
      Test5 > 21 & is.na(LENAD2DataW1) ~ "Delinquent",
      Test5 <= 21 & Test5 >= 14 & is.na(LENAD2DataW1) ~ "Warning",
      Test5 < 14 & is.na(LENAD2DataW1) ~ "On-Track",
      LENAD2DiaryActual > start & is.na(LENAD2DataW1) ~ "Delinquent",
      LENAD2DataW1 > 0       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment8 <- Enrollment7.1%>%
      select(RSID:LENAD2DataStatus) %>%
      mutate(
      Surv3Status = case_when(
      DropOutStage > 0 & is.na(Survey3Actual) ~ "Opt-Out",
      Survey3_OptOut > start  ~ "Opt-Out",
      Test6 > 7 & is.na(Survey3Actual) ~ "Delinquent",
      Test6 <= 7 & Test6 >= 3 & is.na(Survey3Actual) ~ "Warning",
      Test6 < 3 & is.na(Survey3Actual) ~ "On-Track",
      Survey4Actual > start & is.na(Survey3Actual) ~ "Delinquent",
      PDR5Actual > start & is.na(Survey3Actual) ~ "Delinquent",
      PDR6Actual > start & is.na(Survey3Actual) ~ "Delinquent",
      LENAD3DiaryActual > start & is.na(Survey3Actual) ~ "Delinquent",
      LENAD4DiaryActual > start & is.na(Survey3Actual) ~ "Delinquent",
      Survey3Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment9 <- Enrollment8%>%
      select(RSID:Surv3Status) %>%
      mutate(
      Surv4Status = case_when(
      DropOutStage > 0 & is.na(Survey4Actual) ~ "Opt-Out",
      Survey4_OptOut > start  ~ "Opt-Out",
      Test7 > 7 & is.na(Survey4Actual) ~ "Delinquent",
      Test7 <= 7 & Test7 >= 3 & is.na(Survey4Actual) ~ "Warning",
      Test7 < 3 & is.na(Survey4Actual) ~ "On-Track",
      PDR5Actual > start & is.na(Survey4Actual) ~ "Delinquent",
      PDR6Actual > start & is.na(Survey4Actual) ~ "Delinquent",
      LENAD3DiaryActual > start & is.na(Survey4Actual) ~ "Delinquent",
      LENAD4DiaryActual > start & is.na(Survey4Actual) ~ "Delinquent",
      Survey4Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment10 <- Enrollment9%>%
      select(RSID:Surv4Status) %>%
      mutate(
      PDR5Status = case_when(
      DropOutStage > 0 & is.na(PDR5Actual) ~ "Opt-Out",
      PDRW2D2_OptOut > start  ~ "Opt-Out",
      Test8 > 3 & is.na(PDR5Actual) ~ "Delinquent",
      Test8 <= 3 & Test8 >= 1 & is.na(PDR5Actual) ~ "Warning",
      Test8 < 1 & is.na(PDR5Actual) ~ "On-Track",
      PDR6Actual > start & is.na(PDR5Actual) ~ "Delinquent",
      LENAD3DiaryActual > start & is.na(PDR5Actual) ~ "Delinquent",
      LENAD4DiaryActual > start & is.na(PDR5Actual) ~ "Delinquent",
      PDR5Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment11 <- Enrollment10%>%
      select(RSID:PDR5Status) %>%
      mutate(
      PDR6Status = case_when(
      DropOutStage > 0 & is.na(PDR6Actual) ~ "Opt-Out",
      PDRW2D3_OptOut > start  ~ "Opt-Out",
      Test9 > 3 & is.na(PDR6Actual) ~ "Delinquent",
      Test9 <= 3 & Test9 >= 1 & is.na(PDR6Actual) ~ "Warning",
      Test9 < 1 & is.na(PDR6Actual) ~ "On-Track",
      LENAD3DiaryActual > start & is.na(PDR6Actual) ~ "Delinquent",
      LENAD4DiaryActual > start & is.na(PDR6Actual) ~ "Delinquent",
      PDR6Actual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment12 <- Enrollment11%>%
      select(RSID:PDR6Status) %>%
      mutate(
      LENAD3DiaryStatus = case_when(
      DropOutStage > 0 & is.na(LENAD3DiaryActual) ~ "Opt-Out",
      LENAW2D1Log_OptOut > start  ~ "Opt-Out",
      Test10 > 3 & is.na(LENAD3DiaryActual) ~ "Delinquent",
      Test10 <= 3 & Test10 >= 1 & is.na(LENAD3DiaryActual) ~ "Warning",
      Test10 < 1 & is.na(LENAD3DiaryActual) ~ "On-Track",
      LENAD4DiaryActual > start & is.na(LENAD3DiaryActual) ~ "Delinquent",
      LENAD3DiaryActual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment12.1 <- Enrollment12%>%
      select(RSID:LENAD3DiaryStatus) %>%
      mutate(
      LENAD3DataStatus = case_when(
      DropOutStage > 0 & is.na(LENAD1DataW2) ~ "Opt-Out",
      Enrollment12$LENAD3OptOut > start & is.na(LENAD1DataW2) ~ "Opt-Out",
      Test10 > 21 & is.na(LENAD1DataW2) ~ "Delinquent",
      Test10 <= 21 & Test10 >= 14 & is.na(LENAD1DataW2) ~ "Warning",
      Test10 < 14 & is.na(LENAD1DataW2) ~ "On-Track",
      LENAD3DiaryActual > start & is.na(LENAD1DataW2) ~ "Delinquent",
      LENAD1DataW2 > 0       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment13 <- Enrollment12.1%>%
      select(RSID:LENAD3DataStatus) %>%
      mutate(
      LENAD4DiaryStatus = case_when(
      DropOutStage > 0 & is.na(LENAD4DiaryActual) ~ "Opt-Out",
      LENAW2D2Log_OptOut > start  ~ "Opt-Out",
      Test11.1 > 3 & is.na(LENAD4DiaryActual) ~ "Delinquent",
      Test11.1 <= 3 & Test11.1 >= 1 & is.na(LENAD4DiaryActual) ~ "Warning",
      Test11.1 < 1 & is.na(LENAD4DiaryActual) ~ "On-Track",
      LENAD4DiaryActual > start       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment13.1 <- Enrollment13%>%
      select(RSID:LENAD4DiaryStatus) %>%
      mutate(
      LENAD4DataStatus = case_when(
      DropOutStage > 0 & is.na(LENAD2DataW2) ~ "Opt-Out",
      LENAD4OptOut > start & is.na(LENAD2DataW2) ~ "Opt-Out",
      Test11.1 > 21 & is.na(LENAD2DataW2) ~ "Delinquent",
      Test11.1 <= 21 & Test11.1 >= 14 & is.na(LENAD2DataW2) ~ "Warning",
      Test11.1 < 14 & is.na(LENAD2DataW2) ~ "On-Track",
      LENAD2DiaryActual > start & is.na(LENAD2DataW2) ~ "Delinquent",
      LENAD2DataW2 > 0       ~ "Complete",
      TRUE                      ~ "NA"
      )
     )
Enrollment14 <- gather(Enrollment13.1, "Instrument", "Status", ConsentStatus, PostConsentStatus, Surv1Status, Surv2Status,PDR2Status, PDR3Status,LENAD1DiaryStatus,LENAD1DataStatus, LENAD2DiaryStatus,LENAD2DataStatus, Surv3Status, Surv4Status,PDR5Status, PDR6Status,LENAD3DiaryStatus,LENAD3DataStatus, LENAD4DiaryStatus, LENAD4DataStatus)
Enrollment15 <- data.frame("RSID" = Enrollment14$RSID, "Instrument" = Enrollment14$Instrument, "Status" = Enrollment14$Status)
Enrollment15$Status <- factor(Enrollment15$Status, levels = c("Complete", "Opt-Out", "On-Track", "Warning",  "Delinquent", "NA"))
Enrollment15$Status <- forcats::fct_relevel(Enrollment15$Status,"Complete", "Opt-Out", "On-Track", "Warning",  "Delinquent", "NA")

Enrollment15$Cases <- factor(Enrollment15$RSID) # Create a categorical variable
Enrollment15$Instrument <- factor(Enrollment15$Instrument, levels = c("ConsentStatus", "PostConsentStatus", "Surv1Status","Surv2Status","PDR2Status","PDR3Status", "LENAD1DiaryStatus","LENAD1DataStatus","LENAD2DiaryStatus","LENAD2DataStatus", "Surv3Status","Surv4Status","PDR5Status","PDR6Status", "LENAD3DiaryStatus","LENAD3DataStatus", "LENAD4DiaryStatus", "LENAD4DataStatus")) # Create categorical variable

#Wave Progression definitions
ConsentComp<- (Enrollment13.1$ConsentStatus== "Complete")
ConsentComp <- length(grep("TRUE", ConsentComp))
ConsentInProg<- (Enrollment13.1$ConsentStatus != "Complete")
ConsentInProg <- length(grep("TRUE", ConsentInProg))
PostConsentComp<- (Enrollment13.1$PostConsentStatus == "Complete" | Enrollment13.1$PostConsentStatus == "Opt-Out")
PostConsentComp<- length(grep("TRUE", PostConsentComp))
PostConsentInProg<- ((Enrollment13.1$PostConsentStatus == "Delinquent"))
PostConsentInProg <- length(grep("TRUE", PostConsentInProg))
Wv1DropOut <- (Enrollment13.1$DropOutStage == 1)
Wv1DropOut <- length(grep("TRUE", Wv1DropOut))
Wv1Comp<- ((Enrollment13.1$LENAD2DiaryStatus == "Complete" | Enrollment13.1$LENAD2DiaryStatus == "Opt-Out") & (Enrollment13.1$DropOutStage != 1 | is.na(Enrollment13.1$DropOutStage)))
Wv1Comp <- (length(grep("TRUE", Wv1Comp))) 
Wv1InProg<- (Enrollment13.1$DropOutStage != 1 | is.na(Enrollment13.1$DropOutStage)) & (Enrollment13.1$LENAD2DiaryStatus == "NA" | Enrollment13.1$LENAD2DiaryStatus == "On-Track" | Enrollment13.1$LENAD2DiaryStatus == "Delinquent" | Enrollment13.1$LENAD2DiaryStatus == "Warning")
Wv1InProg <- length(grep("TRUE", Wv1InProg))
IntvComp<- (Enrollment13.1$FidelityDate > "2020-07-01")
IntvComp <- length(grep("TRUE", IntvComp))
IntvDropOut <- (Enrollment13.1$DropOutStage == 2)
IntvDropOut <- length(grep("TRUE", IntvDropOut))
IntvInProg<- (is.na(Enrollment13.1$FidelityDate) & (Enrollment13.1$DropOutStage != 2 | Enrollment13.1$DropOutStage != 1)) & (Enrollment13.1$LENAD2DiaryStatus == "Complete" | Enrollment13.1$LENAD2DiaryStatus == "Opt-Out")
IntvInProg <- (length(grep("TRUE", IntvInProg)))
Wv2DropOut <- (Enrollment13.1$DropOutStage == 3)
Wv2DropOut <- length(grep("TRUE", Wv2DropOut))
Wv2Comp<- ((Enrollment13.1$FidelityDate > "2020-07-01") & (Enrollment13.1$LENAD4DiaryStatus == "Complete" | Enrollment13.1$LENAD4DiaryStatus == "Opt-Out")) 
Wv2Comp <- (length(grep("TRUE", Wv2Comp)) - (Wv2DropOut))
Wv2InProg<- ((Enrollment13.1$FidelityDate > "2020-07-01") & (Enrollment13.1$LENAD4DiaryStatus == "NA" | Enrollment13.1$LENAD4DiaryStatus == "Delinquent" | Enrollment13.1$LENAD4DiaryStatus == "Warning" | Enrollment13.1$LENAD4DiaryStatus == "On-Track") & (Enrollment13.1$DropOutStage > 3 | is.na(Enrollment13.1$DropOutStage)))
Wv2InProg <- length(grep("TRUE", Wv2InProg))
Wv3DropOut <- (Enrollment13.1$DropOutStage == 4)
Wv3InProg<- Wv2Comp
Wv3DropOut <- length(grep("TRUE", Wv3DropOut))
TotalInProg<- sum(Wv1InProg,IntvInProg, Wv2InProg, Wv3InProg)
TotalDropOuts<- sum(Wv1DropOut,IntvDropOut,Wv2DropOut)
```
<center>
<div class="btn-group btn-group-justified">
  <div class="btn-group">
<button type="button" class="btn btn-outline-dark .w-100">**Consents Complete**<br>`r ConsentComp`</button>
  </div>
  
  <div class="btn-group">
<button type="button" class="btn btn-outline-dark .w-100">**Consents In Progress**<br>`r ConsentInProg`</button>
  </div>
  
</div>

<div class="btn-group btn-group-justified">
  <div class="btn-group">
<a href="#" class="btn btn-default">**Post-Consent Complete**<br>`r PostConsentComp`</a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-default">**Post-Consent In Progress**<br>`r PostConsentInProg`</a>
  </div>
  
</div>
  
<div class="btn-group btn-group-justified">
 <div class="btn-group">
<a href="#" class="btn btn-primary">**Wave 1 Complete**<br>`r Wv1Comp`</a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-primary">**Wave 1 In Progress**<br>`r Wv1InProg`</a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-primary">**Wave 1 Drop-Outs**<br> `r Wv1DropOut` </a>
  </div>
  
</div>

<div class="btn-group btn-group-justified">
 <div class="btn-group">
<a href="#" class="btn btn-success">**Intervention Complete**<br>`r IntvComp`</a>
  </div>
 <div class="btn-group">
<a href="#" class="btn btn-success">**Intervention In Progress**<br>`r IntvInProg`</a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-success">**Intervention Drop-Outs**<br>`r IntvDropOut` </a>
  </div>
  
</div>

<div class="btn-group btn-group-justified">
 <div class="btn-group">
<a href="#" class="btn btn-info">**Wave 2 Complete**<br>`r Wv2Comp`</a>
  </div>
 <div class="btn-group">
<a href="#" class="btn btn-info">**Wave 2 In Progress**<br>`r Wv2InProg`</a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-info">**Wave 2 Drop-Outs**<br>`r Wv2DropOut` </a>
  </div>
  
</div>

<div class="btn-group btn-group-justified">
 <div class="btn-group">
<a href="#" class="btn btn-warning">**Wave 3 Complete**<br>TBD</a>
  </div>
 <div class="btn-group">
<a href="#" class="btn btn-warning">**Wave 3 In Progress**<br>`r Wv3InProg`</a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-warning">**Wave 3 Drop-Outs**<br>`r Wv3DropOut` </a>
  </div>
  
</div>

<div class="btn-group btn-group-justified">
 <div class="btn-group">
<a href="#" class="btn btn-danger">**Total Complete with Study**<br>TBD</a>
  </div>
 <div class="btn-group">
<a href="#" class="btn btn-danger">**Total In Progress**<br> `r TotalInProg` </a>
  </div>
  
  <div class="btn-group">
<a href="#" class="btn btn-danger">**Total Drop-Outs**<br>`r TotalDropOuts`</a>
  </div>
  
</div>

</div>
<br>
<br>
<center>

```{r SEAL Wave Progression, echo = FALSE, fig.width=5, fig.height=4, message=FALSE, warning=FALSE}
par(mar = c(4, 4, .2, .1))
#Wave_Progression <- Enrollment %>%
 # dplyr::mutate(month = format(SubInfoActual, "%m")) %>%
  #dplyr::group_by(Survey1Completion, Survey2Completion, PDR2Completion, PDR3Completion, #LENAD1DiaryCompletion, LENAD1DataCompletion, LENAD2DiaryCompletion, LENAD2DataCompletion, #CoachImpCompletion, Survey3Completion, Survey4Completion, PDR5Completion, PDR6Completion, #LENAD3DiaryCompletion, LENAD3DataCompletion, LENAD4DiaryCompletion, #LENAD4DataCompletion,) %>%
 # dplyr::summarize(Count = n())
 
#library(kableExtra)
 # kable(Wave_Progression,
  #      col.names = c("Survey 1","Survey 2","PDR 2", "PDR 3", "LENA D1 Diary", "LENA D1 #Data", "LENA D2 Diary", "LENA D2 Data", "Intervention","Survey 3","Survey 4","PDR 5", #"PDR 6", "LENA D3 Diary", "LENA D3 Data","LENA D4 Diary","LENA D4 Data", "Number #Complete")) %>%
 #       kable_minimal()
```

<center>
**Participant Progression **  
This chart shows the number of participants complete with each survey instrument across Wave 1 and 2.  
<center>
::: {}
```{r SEAL Wave 1 Progression, echo = FALSE, fig.width=10, fig.height=4, message=FALSE, warning=FALSE}

p <- ggplot(data = Enrollment15, aes(x=Instrument, fill= forcats::fct_rev(Status))) + geom_bar() + 
# Creates stacked bar chart
scale_x_discrete(label=c("Consent","PostConsentStatus", "Survey 1", "Survey 2", "PDR2", "PDR3", "LENA D1 Diary", "LENA D1 Data","LENA D2 Diary", "LENA D2 Data", "Survey 3", "Survey 4", "PDR5", "PDR6", "LENA D3 Diary", "LENA D3 Data", "LENA D4 Diary", "LENA D4 Data"), drop = FALSE) + scale_fill_manual(values = c("#bdbdbd","#e31a1c","#ffff99","#1f78b4","#737373","#33a02c"
                             ), labels = c("NA", "Delinquent", "Warning", "On-Track", 
                                            "Opt-Out","Complete"), drop = FALSE) #Manually assigns colors
p <- p + xlab("Instrument") + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) + labs(fill = "Statuses") 
 # Adds title and labels
p
```

```{r SEAL Wave 1 Progression Table, echo = FALSE, fig.width=5, fig.height=4, message=FALSE, warning=FALSE}
Wave1 <- table(Enrollment15$Instrument, Enrollment15$Status, dnn=c("Instrument", "Status"))
library(kableExtra)
rownames(Wave1) = c("Consent", "Post Consent", "Survey 1", "Survey 2", "PDR2", "PDR3", "LENA D1 Diary", "LENA D1 Data", "LENA D2 Diary", "LENA D2 Data","Survey 3", "Survey 4", "PDR5", "PDR6", "LENA D3 Diary", "LENA D3 Data", "LENA D4 Diary", "LENA D4 Data")
Wave1Counts <- kable(Wave1,
        col.names = c("Complete","Opt-Out","On-Track", "Warning","Delinquent", "NA")) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
Wave1Counts
```
:::